Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-10 bbbq_article.tex
Figures 1 and 2 refer to tables

Figure \ref{fig:1} shows the percentages of MHC-I epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.

The KS test to determine if MHC-I has the same percentage 
of epitopes overlapping with viral TMHs, 
compared to human TMHs \richel{$\mathcal{H}_{1,V}$},
resulted in a p-value of \richel{unknown},
which makes us [reject/accept] the hypothesis that these percentages
are sampled from the same distribution.

The KS test to determine if MHC-I has the same percentage 
of epitopes overlapping with bacterial TMHs, 
compared to human TMHs \richel{$\mathcal{H}_{1,B}$},
resulted in a p-value of \richel{unknown},
which makes us [reject/accept] the hypothesis that these percentages
are sampled from the same distribution.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    Epitope prediction by EpitopePrediction.
  }
  \label{fig:1}
\end{figure}

@@

Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (tables \ref{tab:tmh_binders_mhc1} 
and \ref{tab:tmh_binders_mhc2}) for the TMH and epitope counts.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, SARS-CoV-2 (labeled 'covid') 
    and Mycobacterium tuberculosis (labeled 'myco') proteome,
    Epitope prediction by NetMHCIIpan.
  }
  \label{fig:2}
\end{figure}

>>>>

Figure \ref{fig:1} shows the percentages of MHC-I epitopes overlapping 
with TMHs for our human, viral and bacterial proteome,
when using EpitopePrediction to predict epitopes.
See the supplementary materials (table \ref{tab:tmh_binders_mhc1}) 
for the TMH and epitope counts.

% The KS test to determine if MHC-I has the same percentage 
% of epitopes overlapping with viral TMHs, 
% compared to human TMHs \richel{$\mathcal{H}_{1,V}$},
% resulted in a p-value of \richel{unknown},
% which makes us [reject/accept] the hypothesis that these percentages
% are sampled from the same distribution.

% The KS test to determine if MHC-I has the same percentage 
% of epitopes overlapping with bacterial TMHs, 
% compared to human TMHs \richel{$\mathcal{H}_{1,B}$},
% resulted in a p-value of \richel{unknown},
% which makes us [reject/accept] the hypothesis that these percentages
% are sampled from the same distribution.

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    Epitope prediction by EpitopePrediction.
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
  }
  \label{fig:1}
\end{figure}

@@

Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc2}) 
for the TMH and epitope counts.

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, SARS-CoV-2 (labeled 'covid') 
    and Mycobacterium tuberculosis (labeled 'myco') proteome,
    Epitope prediction by NetMHCIIpan.
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
  }
  \label{fig:2}
\end{figure}
